Optimized Multi-Frequency Spectra for Numerical Radiative Transfer

### 2011-09-03 doc/paper/ms.tex
Everything is looking good.  Time to run big resolution suite.

In the remainder of this section, we will focus on two simple test problems.  First, the standard case of ionization and heating surrounding a $10^5$ K blackbody (test problem 2 in RT06), and second, the identical scenario for a power-law emitting X-ray source.  Initially, we will consider each case in a hydrogen-only medium, and include the effects of helium shortly thereafter.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{figures/RT_Test1_IfrontEvolution.ps}
\vspace{-20pt}
\caption{\textit{Top:} Comparison of the calculated (dashed) and analytic (solid) positions of an expanding ionization front in a hydrogen-only, isothermal medium. \textit{Bottom:} Ratio of the calculated and analytic solutions.}
\label{fig:RT_Test1_IfrontEvolution}
\end{center}
\end{figure}

>>>>

In the remainder of this section, we will focus on two simple test problems.  First, the standard case of ionization and heating surrounding a $10^5$ K blackbody (problem \#2 in RT06), and second, the identical scenario for a power-law emitting X-ray source.  Initially, we will consider each case in a hydrogen-only medium, and later include the effects of helium.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.4]{figures/RT_Test1_IfrontEvolution.ps}
\vspace{-20pt}
\caption{\textit{Top:} Comparison of the calculated (dashed) and analytic (solid) positions of an expanding ionization front in a hydrogen-only, isothermal medium. \textit{Bottom:} Ratio of the calculated and analytic solutions.}
\label{fig:RT_Test1_IfrontEvolution}
%\end{center}
\end{figure}
